Stats for the convergence paper

### 2019-07-02 models/paper/convergence_paper_models.Rmd
effects

library(brms)
library(lme4)
library(tidyverse)
options(mc.cores=parallel::detectCores())
# options(mc.cores=1)
Sys.setenv(TZ="Europe/Rome") # a szivemben örök tavasz van

try(setwd('../../models/paper'))
try(setwd('~/Github/RaczBecknerHayPierrehumbert2019/models/paper'))
```

@@

```{r }
source('../../functions/grabdata.R')

@@

```{r }
test2$lex_typicality = factor(test2$lex_typicality, levels = c('typical', 'random', 'atypical'))
test2$reg_rate = factor(test2$reg_rate, levels = c('-40%', 'nc', '+40%'))
test2$baseline_av_z = scales::rescale(test2$baseline_av)
test2$pre_reg_av_z = scales::rescale(test2$pre_reg_av)

@@

load('../../models/paper/bayes_fit3.rda')
bayes_factor()

load('../../models/paper/loo_comparisons.rda')
loo.comparisons

@@

fit3b = brm(resp_post_reg ~ 1 + baseline_av_z * lex_typicality + pre_reg_av_z + reg_rate +
    (1 + baseline_av_z | participant_id) + 
    (1 + pre_reg_av_z | word), 
  data = test2b, 
  family = bernoulli, 
  control=list(adapt_delta=0.99, stepsize = 0.01, max_treedepth =15), save_all_pars = T)

fit3c = brm(resp_post_reg ~ 1 + baseline_av_z + pre_reg_av_z + reg_rate +
    (1 + baseline_av_z | participant_id) + 
    (1 + pre_reg_av_z | word), 
  data = test2b, 
  family = bernoulli, 
  control=list(adapt_delta=0.99, stepsize = 0.01, max_treedepth =15), save_all_pars = T)

save(fit3b, file = 'fit3b.rda')
save(fit3c, file = 'fit3c.rda')

@@

```{r }
load('fit3b.rda')
load('fit3c.rda')

bf = bayes_factor(fit3c, fit3b)
bf$bf
# time to ask for help.
```

>>>>

library(brms)
library(lme4)
library(merTools)
library(tidyverse)
options(mc.cores=parallel::detectCores())
# options(mc.cores=1)
Sys.setenv(TZ="Europe/Rome") # a szivemben örök tavasz van

try(setwd('~/Work/NZILBB/RaczBecknerHayPierrehumbert2019'))
try(setwd('~/Github/RaczBecknerHayPierrehumbert2019'))
```

@@

```{r }
source('functions/grabdata.R')

@@

```{r }
test2$lex_typicality = factor(test2$lex_typicality, levels = c('typical', 'random', 'atypical'))
test2$reg_rate = factor(test2$reg_rate, levels = c('nc', '-40%', '+40%'))
test2$baseline_av_z = scales::rescale(test2$baseline_av)
test2$pre_reg_av_z = scales::rescale(test2$pre_reg_av)
test2$baseline_av_c = test2$baseline_av - mean(test2$baseline_av)
test2$pre_reg_av_c = test2$pre_reg_av - mean(test2$pre_reg_av)

@@

load('models/paper/bayes_fit3.rda')
bayes_factor()

load('../../models/paper/loo_comparisons.rda')
loo.comparisons
```

@@

fit_power1 = glmer(resp_post_reg ~ 1 + baseline_av_c * lex_typicality + pre_reg_av_c + reg_rate +
    (1 + baseline_av_c | participant_id) + 
    (1 | word), 
  data = test2b, 
  family = binomial ( link = logit ),
  control=glmerControl(optimizer="bobyqa")
  )

fit_power2 = glmer(resp_post_reg ~ 1 + baseline_av_c + lex_typicality + pre_reg_av_c + reg_rate +
    (1 + baseline_av_c | participant_id) + 
    (1 | word), 
  data = test2b, 
  family = binomial ( link = logit ),
  control=glmerControl(optimizer="bobyqa")
  )

# summary(fit_power1)
# summary(fit_power2)

exp((BIC(fit_power2) - BIC(fit_power1))/2)
# 0.01179529
# we favour the null model

@@

The lme4 fit reported in the paper is here.

```{r }
# the frequentist fit reported in the paper
# watch out for factor levels
# lex typ: typical - random - reversed
# reg shift: nc - -40% - +40%
lme.fit2 = glmer(resp_post_reg ~ 1 + baseline_av_c * lex_typicality + pre_reg_av_c + reg_rate +
    (1 + baseline_av_c | participant_id) + 
    (1  | word), 
  data = test2, 
  family = binomial (link = logit),
  control=glmerControl(optimizer="bobyqa")
)
summary(lme.fit2)$coef %>% 
  xtable

Let's have a few estimates for CI-s.

```{r }
lme.fit2.preds = predictInterval(merMod = lme.fit2, level = 0.95, n.sims = 1000, stat = 'median', type = 'probability')

test2c = cbind(test2,lme.fit2.preds) 
test2c %>%   
  group_by(
    reg_rate
  ) %>% 
  summarise(
    fit = mean(fit),
    upr = mean(upr),
    lwr = mean(lwr)
  ) %>% 
  ggplot(aes(x = reg_rate, y = fit)) +
  geom_point() +
  geom_linerange(aes(ymin = lwr, ymax = upr))

confint(lme.fit2, method = 'Wald', level = 0.95)
effects::allEffects(lme.fit2)
```
